---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# HIBPwned
[![Travis-CI Build Status](https://travis-ci.org/stephlocke/HIBPwned.svg?branch=master)](https://travis-ci.org/stephlocke/HIBPwned)
[![Coverage Status](https://coveralls.io/repos/github/stephlocke/HIBPwned/badge.svg?branch=master)](https://coveralls.io/github/stephlocke/HIBPwned?branch=master)
[![Total CRAN downloads](http://cranlogs.r-pkg.org/badges/grand-total/HIBPwned)](http://cranlogs.r-pkg.org/badges/grand-total/HIBPwned)

Utilising the [HaveIBeenPwned.com API](https://haveibeenpwned.com/API/v2), check whether email addresses and/or user names have been present in a publicly disclosed data breach.

## News
HaveIBeenPwned is now rate limited to one request per 1.5 seconds. To facilitate this, I added a Sleep command. This was inelegant. Instead, the package now relies on the package [ratelimitr](https://github.com/tarakc02/ratelimitr) to perform rate limiting.

## Tests
```{r}
devtools::test()
```

----

If you get a lot of value out of this package, do consider donating to [HaveIbeenPwned.com](https://haveibeenpwned.com/Donate) as it's a tremendous service.

----

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

----

## Usage

```{r, results='hide', message=FALSE, warning=FALSE}
if(!require("devtools")) install.packages("devtools")
# Get or upgrade from github
devtools::install_github("stephlocke/HIBPwned")
library("HIBPwned")
```

```{r}
account_breaches("foo@bar.com", truncate=TRUE)
```

```{r}
breached_sites("adobe.com")
```

```{r}
breached_site("Adobe")
```

```{r}
data_classes()
```

```{r}
pastes("foo@bar.com")
```

